Minimizing post-shock forecasting error using disparate information

### 2020-07-07 manuscript/manuscript.tex
addition of simulation discussions

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=1in}

@@

Things to do:
\begin{enumerate}
  \item Need to add simulations. 
\end{enumerate}

@@

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
  \item Addition of Section 3.4
\end{enumerate}

@@

for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = 1(t = T_i^* + 1)$, 

@@

However, LOOCV can be very computationally intensive when $n$ is large. In an analog to $k$-fold cross-validation as remedies for ordinary LOOCV, we propose a similar procedure \emph{LOOCV with $k$ random draws} to alleviate the computation burden. LOOCV with $k$ random draws differs in the selection of indices. The algorithms are outlined as follows. If $n \leq  k$, we set $k$ to be $n$. If $n > k$, we randomly sample without replacement $k$ elements from $\{1, \ldots, n\}$ to gather them into $\mc{J}$. For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$. The LOOCV with $k$ random draws estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
\begin{align*}
	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
	 \quad \text{ and } \quad \bar{\mc{C}}^{(k)}(\mc{A})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\mc{A}).
\end{align*}
Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}^{}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively. The estimation bias should decrease as $k \to n$.  In practice, $k=5$ or $k=10$ can be typical choices for LOOCV with $k$ random draws.

@@

In this section, we provide justification for our methods based on Monte Carlo simulation examples. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$. Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

@@

In this section, we provide justification for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}). We will compare the result of using parametric bootstrap conditioned on the donor pool with the one without using the parameter setup discussed in Section \ref{simulation}.

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma$ to $10$. From Table ?, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we can observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small. It is because when $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal. Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}. Nevertheless, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$. It is to be expected since the bootstrap estimates become more biased. However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$. Fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases. It is due to the robustness gain in estimation when $n$ increases.

In this setting, comparing Table ? with Table ??, we can see that $\mc{B}_u$ does not differ a lot from $\mc{B}_c$.

\subsection{Simulation for prediction}

In this section, we report prediction results for our methods in the simulation. Specifically, we are interested in the distance between $\alpha_1$ and our shock-effect estimators, and the distance between $y_{1,T_1^*+1}$ and $\hat{y}_{1,T_1^*+1}$, $\hat{y}_{1,T_1^*+1}+ \hat{\alpha}_{\rm adj}$, $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm wadj}$, and $\hat{y}_{1,T_1^*+1}+\hat{\alpha}_{\rm IVW}$.

In the first experiment, Table ? shows similar results to  Section  \ref{parametricbootstrapsimulation} that the prediction and distance to $\alpha_1$ gets better as $n$ increases but worser when the variance of $\alpha_i$ gets larger.

>>>>

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=0.8in}

@@

@@

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
  \item Addition of Section 3.4
  \item A major addition of content to simulation.
\end{enumerate}

@@

for $t = 1,\ldots,T_i$ and $i = 1,\ldots, n+1$, where $D_{i,t} = I(t = T_i^* + 1)$, 

@@

However, LOOCV can be very computationally intensive when $n$ is large. In an analog to $k$-fold cross-validation as remedies for ordinary LOOCV, we propose a similar procedure \emph{LOOCV with $k$ random draws} to alleviate the computation burden. LOOCV with $k$ random draws differs in the selection of indices. The algorithms are outlined as follows. If $n \leq  k$, we set $k$ to be $n$. If $n > k$, we randomly sample without replacement $k$ elements from $\{1, \ldots, n\}$ to gather them into $\mc{J}$. For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$. The LOOCV with $k$ random draws estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
\begin{align*}
	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
	 \quad \text{ and } \quad \bar{\mc{C}}^{(k)}(\mc{A})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\mc{A}).
\end{align*}
Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively. The estimation bias should decrease as $k \to n$.  In practice, $k=5$ or $k=10$ can be typical choices for LOOCV with $k$ random draws.

@@

In this section, we provide justification for our methods based on Monte Carlo simulation examples. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=13$ and $\mu_{\alpha}=2$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}. Parameter setup of our simulations is detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$. Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated the covariates from $\Gamma(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well. Last, we set $\gamma_i, \delta_i\simiid  \normal{1}{0.5}$ and $\theta_i, \beta_i \sim \normal{0}{1}$.

@@

In this section, we discuss simulation results for the bootstrap procedures used in estimating parameters for risk-reduction propositions (see Section \ref{properties}) and risk-reduction quantities (see Section \ref{comparisons}). We will compare $\mc{B}_c$ with $\mc{B}_u$.

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma$ to $10$. Note that $\E{\E{\alpha_1}}=54$, where the last expectation is operated under the density of the covariates. In other words, data with $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$  should well represent the situations when the signal of the covariates is strong and when it is nearly lost.

\begin{table}[t]
\caption{30 Monte Carlo simulations for $\mc{B}_c$ with varying $n$ and $\sigma_{\alpha}$ (risk-reduction propositions $\delta_{\hat{\alpha}}$)} \vspace{.2cm} \label{table1}
\begin{center}
\begin{tabular}{cc|ccc|cccc}
 $n$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]  
  \hline
  \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.90 (0.02) & 0.89 (0.03) & 0.35 (0.04) \\ 
  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.03) & 0.89 (0.03) & 0.89 (0.03) & 0.37 (0.05) \\ 
  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.83 (0.03) & 0.78 (0.03) & 0.44 (0.05) \\ 
  & 50  & 0.90 (0.06) & 0.97 (0.03) & 0.93 (0.05) & 0.66 (0.04) & 0.65 (0.04) & 0.65 (0.04) & 0.45 (0.06) \\ 
  & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.80 (0.07) & 0.57 (0.04) & 0.53 (0.04) & 0.57 (0.04) & 0.49 (0.05) \\[.3cm]  
  \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.92 (0.02) & 0.91 (0.02) & 0.25 (0.03) \\ 
  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.89 (0.02) & 0.89 (0.03) & 0.89 (0.02) & 0.29 (0.03) \\ 
  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.77 (0.04) & 0.3 (0.04) \\ 
  & 50  & 0.83 (0.07) & 1 (0) & 0.80 (0.07) & 0.59 (0.04) & 0.63 (0.04) & 0.59 (0.04) & 0.37 (0.05) \\ 
  & 100  & 0.80 (0.07) & 0.93 (0.05) & 0.80 (0.07) & 0.47 (0.04) & 0.51 (0.04) & 0.46 (0.04) & 0.41 (0.05) \\[.3cm]  
  \multirow{5}{*}{15} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.93 (0.02) & 0.91 (0.02) & 0.31 (0.05) \\ 
  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.87 (0.02) & 0.89 (0.03) & 0.87 (0.02) & 0.31 (0.04) \\ 
 & 25  & 1 (0) & 1 (0) & 1 (0) & 0.75 (0.03) & 0.78 (0.03) & 0.76 (0.03) & 0.37 (0.04) \\ 
  & 50  & 0.933 (0.05) & 1 (0) & 0.9 (0.06) & 0.61 (0.04) & 0.69 (0.03) & 0.64 (0.04) & 0.41 (0.04) \\ 
  & 100  & 0.67 (0.09) & 1 (0) & 0.63 (0.09) & 0.55 (0.04) & 0.51 (0.04) & 0.55 (0.04) & 0.47 (0.04) \\[.3cm]  
  \multirow{5}{*}{25} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.95 (0.02) & 0.94 (0.02) & 0.95 (0.02) & 0.29 (0.04) \\ 
  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.91 (0.02) & 0.93 (0.02) & 0.30 (0.04) \\ 
  & 25  & 1 (0) & 1 (0) & 1 (0) & 0.78 (0.04) & 0.79 (0.04) & 0.77 (0.04) & 0.31 (0.04) \\ 
  & 50  & 0.90 (0.06) & 1 (0) & 0.9 (0.06) & 0.57 (0.04) & 0.60 (0.04) & 0.58 (0.04) & 0.34 (0.04) \\ 
    & 100  & 0.83 (0.07) & 1 (0) & 0.80 (0.07) & 0.49 (0.04) & 0.48 (0.04) & 0.50 (0.04) & 0.39 (0.03) \\ 
\end{tabular}  
\end{center}
 \vspace{-.5cm}
\end{table}

 Table \ref{table1} shows the results, with the 3rd to 5th column representing the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ (i.e., guess of $\delta_{\hat{\alpha}}$), and the 6th to 9th columns representing the LOOCV consistency and best consistency following notations in Section \ref{loocv}. First, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we  observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small  from Table \ref{table1}. The reasons can be explained as follows. When $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal according to construction of $\hat{\alpha}_{\rm wadj}$ in Section \ref{constructionofestimators}. Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}. However, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$. It is to be expected since the bootstrap estimates become more biased. However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$. Second, fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases. It is due to the robustness gain in estimation when $n$ increases.

\begin{table}[t]
    \caption{30 Monte Carlo simulations for $\mc{B}_c$ with varying $\sigma$ and $\sigma_{\alpha}$} \label{table2} \vspace{-.2cm}
  \begin{center}
\begin{tabular}{cc|ccc|cccc}
 $\sigma$   & $\sigma_{\alpha}$ &  $\hat{\alpha}_{\rm adj}$  & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm adj}})$  & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ & $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm IVW}})$ &  $\bar{\mc{C}}^{(k)}(\mc{A})$ \\[.15cm]  
  \hline
 \multirow{5}{*}{5} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.99 (0.01) & 0.99 (0.01) & 0.99 (0.01) & 0.4 (0.04) \\ 
  & 10  & 1 (0) & 1 (0) & 1 (0) & 0.91 (0.02) & 0.95 (0.02) & 0.92 (0.02) & 0.46 (0.04) \\ 
    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.83 (0.03) & 0.89 (0.02) & 0.83 (0.03) & 0.43 (0.04) \\ 
   & 50  & 0.87 (0.06) & 1 (0) & 0.87 (0.06) & 0.67 (0.04) & 0.69 (0.03) & 0.67 (0.04) & 0.38 (0.04) \\ 
    & 100  & 0.7 (0.09) & 0.93 (0.05) & 0.77 (0.08) & 0.52 (0.04) & 0.51 (0.04) & 0.51 (0.05) & 0.51 (0.05) \\[.3cm] 
    \multirow{5}{*}{10} & 5  & 1 (0) & 1 (0) & 1 (0) & 0.93 (0.02) & 0.93 (0.02) & 0.93 (0.02) & 0.27 (0.03) \\ 
    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.86 (0.03) & 0.89 (0.03) & 0.87 (0.03) & 0.37 (0.04) \\ 
    & 25  & 0.97 (0.03) & 1 (0) & 0.97 (0.03) & 0.78 (0.03) & 0.82 (0.03) & 0.79 (0.03) & 0.29 (0.04) \\ 
    & 50  & 0.93 (0.05) & 1 (0) & 0.9 (0.06) & 0.66 (0.04) & 0.67 (0.04) & 0.66 (0.04) & 0.32 (0.04) \\ 
    & 100  & 0.77 (0.08) & 0.97 (0.03) & 0.7 (0.09) & 0.54 (0.05) & 0.54 (0.04) & 0.55 (0.04) & 0.43 (0.05) \\[.3cm] 
    \multirow{5}{*}{25} & 5  & 0.97 (0.03) & 1 (0) & 1 (0) & 0.78 (0.03) & 0.77 (0.03) & 0.79 (0.03) & 0.22 (0.03) \\ 
    & 10  & 1 (0) & 1 (0) & 1 (0) & 0.81 (0.03) & 0.79 (0.03) & 0.81 (0.03) & 0.21 (0.03) \\ 
    & 25  & 1 (0) & 1 (0) & 1 (0) & 0.72 (0.03) & 0.77 (0.03) & 0.71 (0.03) & 0.25 (0.04) \\ 
    & 50  & 0.87 (0.06) & 0.97 (0.03) & 0.87 (0.06) & 0.55 (0.04) & 0.57 (0.04) & 0.52 (0.04) & 0.35 (0.04) \\ 
    & 100  & 0.9 (0.06) & 1 (0) & 0.87 (0.06) & 0.54 (0.04) & 0.54 (0.04) & 0.56 (0.04) & 0.39 (0.05) \\[.3cm] 
    \multirow{5}{*}{50} & 5  & 0.83 (0.07) & 0.73 (0.08) & 0.8 (0.07) & 0.54 (0.04) & 0.57 (0.04) & 0.55 (0.04) & 0.19 (0.03) \\ 
    & 10  & 0.77 (0.08) & 0.8 (0.07) & 0.77 (0.08) & 0.53 (0.04) & 0.55 (0.05) & 0.53 (0.04) & 0.23 (0.03) \\ 
    & 25  & 0.73 (0.08) & 0.8 (0.07) & 0.73 (0.08) & 0.58 (0.04) & 0.58 (0.04) & 0.57 (0.04) & 0.21 (0.03) \\ 
    & 50  & 0.8 (0.07) & 0.83 (0.07) & 0.8 (0.07) & 0.59 (0.04) & 0.53 (0.04) & 0.6 (0.04) & 0.29 (0.05) \\ 
    & 100  & 0.5 (0.09) & 0.73 (0.08) & 0.53 (0.09) & 0.51 (0.05) & 0.48 (0.05) & 0.51 (0.05) & 0.31 (0.04) \\[.3cm] 
    \multirow{5}{*}{100} & 5  & 0.43 (0.09) & 0.37 (0.09) & 0.43 (0.09) & 0.47 (0.04) & 0.47 (0.04) & 0.47 (0.04) & 0.19 (0.03) \\ 
    & 10  & 0.63 (0.09) & 0.6 (0.09) & 0.67 (0.09) & 0.51 (0.04) & 0.49 (0.04) & 0.51 (0.04) & 0.23 (0.03) \\ 
    & 25  & 0.57 (0.09) & 0.6 (0.09) & 0.57 (0.09) & 0.51 (0.04) & 0.53 (0.04) & 0.49 (0.04) & 0.21 (0.04) \\ 
    & 50  & 0.53 (0.09) & 0.43 (0.09) & 0.5 (0.09) & 0.47 (0.04) & 0.49 (0.05) & 0.49 (0.05) & 0.19 (0.03) \\ 
    & 100  & 0.63 (0.09) & 0.63 (0.09) & 0.63 (0.09) & 0.43 (0.04) & 0.41 (0.04) & 0.45 (0.04) & 0.17 (0.03) \\ 
\end{tabular}
  \end{center}  
   \vspace{-.5cm}
\end{table}

Interestingly, we observe different patterns of $\bar{\mc{C}}^{(k)}(\mc{A})$ as opposed to $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$: (1) as $n$ increases, $\bar{\mc{C}}^{(k)}(\mc{A})$ decreases; and (2) as $\sigma_{\alpha}$ increases, $\bar{\mc{C}}^{(k)}(\mc{A})$ increases. It is possible  when $n$ is small or $\sigma_{\alpha}$ is large, the differences among $\hat{\Delta}(\hat{\alpha})$ for  $\hat{\alpha}\in \mc{A}$ are large so that the ranking gains more precision. It is because in these situations, the estimation of bootstrap estimates is less precise so that the variance of $\hat{\Delta}(\hat{\alpha})$ is larger.

Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.  Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$. But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased}. Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative. Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$. For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.90 \times 0.66 = 0.594$ from table \ref{table1}.  In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.

In the second experiment, we consider the parameter combination of $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $n$ to $10$. Likewise, $\sigma, \sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ will produce situations when the signal of the covariates is strong and when it is nearly lost in the model of  both $y_{i,t}$ and $\alpha_i$.

From Table \ref{table2}, we observe that as $\sigma_{\alpha}$ increases fixing $\sigma$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ will  decrease, which is a pattern similar to one shown in the first experiment. Furthermore, as $\sigma$ increases fixing $\sigma_{\alpha}$, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ decrease as well. Note that the consistency or best consistency  hinges on the estimation of the parameters. Since $\hat{\alpha}_{\rm wadj}$  is a linear combination of OLS estimates, as $\sigma$ increases, $\var{\hat{\alpha}_{\rm wadj}}$ increases as well. Therefore, $\hat{\alpha}_{\rm wadj}$ become more volatile and its estimation of $\E{\alpha_1}$ can be less reliable. Those reasons can explain  why an increase of $\sigma_{\alpha}$ contributes to a decrease of  $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$.

With respect to averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ (i.e., the guess), it starts to decrease as $\sigma$ increases. It is reasonable if we believe the bootstrap estimate $S^2_{\hat{\alpha}}$ provides a good approximation for $\var{\hat{\alpha}}$ for $\hat{\alpha}\in \mc{A}$. The reasons can be outlined as below. Recall in Section \ref{conditionsm2122}, the conditions of risk-reduction propositions involve $(\E{\alpha_1})^2 > \var{\hat{\alpha}} + (\E{\hat{\alpha}}-\E{\alpha_1})^2$ for $\hat{\alpha}\in \mc{A}$, where we note that those parameters are \emph{true} ones but not estimated ones. Notice that $\var{\hat{\alpha}}$ is  a function of $\sigma$ since $\hat{\alpha}$ is estimated by OLS. Therefore, it explains the reason why the increase of $\sigma$ would result in a decrease of averaged $I(\hat{\Delta}(\hat{\alpha}>0)$ since the conditions are not likely to hold when  $\var{\hat{\alpha}}$ increases.

\begin{table}[t]
 \caption{30 Monte Carlo simulation with varying $n$ and $\sigma_{\alpha}$ (distance to $y_{1, T_1^*+1}$)} \label{table3}
 \begin{center}
\begin{tabular}{cc|cccc}
  $n$   & $\sigma_{\alpha}$  & Original & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$\\[.3cm]  
  \hline
  \multirow{5}{*}{5} & 5  & 51.92 (4.04) & 19.23 (2.55) & 20.64 (2.76) & 19.36 (2.52) \\ 
  & 10  &  52.58 (4.35) & 21.565 (2.58) & 23.38 (2.86) & 21.72 (2.50) \\ 
  & 25  &  55.02 (5.84) & 30.30 (3.59) & 31.99 (4.36) & 30.20 (3.50) \\ 
  & 50  & 64.42 (8.11) & 50.00 (5.78) & 52.56 (6.92) & 49.55 (5.70) \\ 
  & 100  & 91.51 (13.20) & 94.27 (10.41) & 97.26 (12.57) & 93.61 (10.27) \\[.3cm]  
  \multirow{5}{*}{10} & 5 & 52.34 (4.00) & 17.23 (2.96) & 18.55 (2.84) & 17.39 (2.95) \\ 
  & 10 &  52.59 (4.05) & 19.02 (3.24) & 20.95 (3.14) & 19.23 (3.24) \\ 
  & 25 & 54.07 (4.97) & 27.66 (4.55) & 31.79 (4.47) & 27.85 (4.61) \\ 
  & 50 &  60.32 (7.53) & 47.70 (7.04) & 52.97 (7.54) & 47.78 (7.17) \\ 
  & 100 & 85.60 (12.99) & 89.86 (12.82) & 100.74 (13.61) & 90.40 (12.91) \\[.3cm]  
  \multirow{5}{*}{15} & 5 & 49.86 (4.01) & 18.07 (2.88) & 18.38 (2.71) & 18.04 (2.88) \\ 
  & 10 & 48.73 (4.30) & 19.45 (2.97) & 19.35 (2.86) & 19.32 (3.00) \\ 
  & 25 &  47.06 (5.13) & 26.16 (3.31) & 26.81 (3.13) & 26.23 (3.33) \\ 
  & 50 &  48.75 (6.86) & 40.27 (4.43) & 42.09 (4.49) & 40.77 (4.38) \\ 
  & 100 &  64.29 (11.11) & 68.85 (8.27) & 74.08 (8.72) & 69.91 (8.14) \\[.3cm]  
  \multirow{5}{*}{25} & 5 & 57.60 (6.94) & 21.58 (5.90) & 20.00 (5.86) & 21.58 (5.90) \\ 
  & 10 &  56.80 (7.01) & 22.20 (5.97) & 20.47 (5.89) & 22.22 (5.97) \\ 
  & 25 &  56.58 (7.49) & 28.96 (6.49) & 27.06 (6.19) & 29.03 (6.48) \\ 
  & 50 &  64.33 (8.75) & 47.16 (8.28) & 46.30 (7.26) & 47.35 (8.26) \\ 
  & 100 & 95.61 (13.02) & 90.10 (13.29) & 86.81 (11.75) & 90.55 (13.23) \\ 
\end{tabular}	
 \end{center}
 \vspace{-.5cm}
\end{table}

Simulation for $\mc{B}_u$ with the same parameter setup as that of $\mc{B}_c$ are implemented. See table \ref{table6} and table \ref{table7} for results. Comparing table \ref{table1}
 and table \ref{table6} yields that when $n$ is small ($n = 5$ or $n = 10$) and $\sigma_{\alpha}$ is small ($\sigma_{\alpha}=5$), $\mc{B}_u$ is better than $\mc{B}_c$ with statistical evidence. For other situations, $\mc{B}_u$  and $\mc{B}_c$  are rather similar. It is likely that the extra randomness from sampling with replacement from donor pool compensates for the possible noises from a small donor pool. Concerning  table \ref{table2} and table \ref{table7}, it appears that when $n = 10$ and $\sigma_{\alpha}=5$, $\mc{B}_u$ is better than  $\mc{B}_c$  when $\sigma$ increases. It might be the case that additional layer of bootstrap in the donor pool buffers the negative effects on $\bar{\mc{C}}(\delta_{\hat{\alpha}})$  introduced from increasing variation of $y_{i,t}$. However, when $\sigma_{\alpha}$ increases over 5 and $n = 10$,  $\mc{B}_c$ and $\mc{B}_u$ are quite similar under  situations of different $\sigma$ and $\sigma_{\alpha}$. In conclusion, $\mc{B}_u$ is better than $\mc{B}_c$ when the signal of the covariates is strong and $n$ is small; otherwise, they are similar. See more discussions for differences between $\mc{B}_u$ and $\mc{B}_c$ in Section \ref{discussion}.

\subsection{Simulation for prediction}
\label{simulationforprediction}
